Extended Data

### 2022-03-13 doc/manuscript/Dow_manuscript_Nature.Rmd
remove results paragraph comparing sites & species groups
@camerondow35 , on second thought, I think you were right that we could remove the comparison of sites, and also species groups. (I'd keep all or none.)

See what you think.

Using dendrometer band measurements taken throughout multiple growing seasons at the Smithsonian Conservation Biology Institute (SCBI; Virginia, USA; n = `r n_dendro_trees_SCBI` trees from 2011-2020) and Harvard Forest (Massachusetts, USA; n = `r n_dendro_trees_HF` trees from 1998-2003), we fit a logistic growth model[@mcmahon_general_2015] to determine the days of year (DOY) when 25, 50, and 75% annual growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$), peak growing season length ($L_{pgs}= DOY_{75}$-$DOY_{25}$), the maximum daily growth rates ($g_{max}$; occurs on average within 5 days of $DOY_{50}$), and total annual increment in diameter at breast height ($\Delta DBH$; Fig. `r schematic_summary`). 
This analysis was performed separately for ring- (67 trees at SCBI and 138 trees at Harvard Forest) and diffuse porous (52 trees at SCBI and 183 trees at Harvard Forest) species, which differ in the seasonal timing of growth[@dorangeville_peak_2021;@tumajer_limitation_2022]. 
These stem-growth milestones were compared to canopy foliage phenology (measured at ecosystem level via remote sensing).

@@

Seasonal milestones for both canopy foliage phenology and stem growth occurred 3-16 days earlier at SCBI than at Harvard Forest (Fig. `r DOY_timing`, `r  EDT_phenology_parameters`).<!--cool to note, but is it necessary? Especially considering how broad "seasonal milestones for BOTH..." is. KAT: I'd like to try to keep it in because it links to I think we should keep it in because it links-->
Consistent with the results of Ref[@dorangeville_peak_2021], ring porous species began growing earlier, reaching the $DOY_{25}$ benchmark earlier (by `r 155-128` days at SCBI and `r 166-144` at Harvard Forest), and their growth was spread over a longer growing season (average $L_{PGS}$ 22 and 17 days longer at SCBI and Harvard Forest, respectively; Fig. `r DOY_timing`, `r  EDF_growth_curves_all`, `r  EDT_phenology_parameters`). 
Peak growing season length was similar across sites, with $L_{PGS}$ being, on average, only six days longer at SCBI for ring porous species and less than one day longer for diffuse porous species (`r  EDT_phenology_parameters`).

>>>>

Using dendrometer band measurements taken throughout multiple growing seasons at the Smithsonian Conservation Biology Institute (SCBI; Virginia, USA; n = `r n_dendro_trees_SCBI` trees from 2011-2020) and Harvard Forest (Massachusetts, USA; n = `r n_dendro_trees_HF` trees from 1998-2003), we fit a logistic growth model[@mcmahon_general_2015] to determine the days of year (DOY) when 25, 50, and 75% annual growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$), peak growing season length ($L_{pgs}= DOY_{75}$-$DOY_{25}$), the maximum daily growth rates ($g_{max}$; occurs on average within 5 days of $DOY_{50}$), and total annual increment in diameter at breast height ($\Delta DBH$; Fig. `r schematic_summary`). 
This analysis was performed separately for ring- <!--(67 trees at SCBI and 138 trees at Harvard Forest)-->and diffuse porous <!--(52 trees at SCBI and 183 trees at Harvard Forest)-->species (`r EDT_species`), which differ in the seasonal timing of growth(`r  EDT_phenology_parameters`)[@dorangeville_peak_2021;@tumajer_limitation_2022]. 
These stem-growth milestones were compared to canopy foliage phenology (measured at ecosystem level via remote sensing).

@@

<!--Seasonal milestones for both canopy foliage phenology and stem growth occurred 3-16 days earlier at SCBI than at Harvard Forest (Fig. `r DOY_timing`, `r  EDT_phenology_parameters`).-->
<!--Consistent with the results of Ref[@dorangeville_peak_2021], ring porous species began growing earlier, reaching the $DOY_{25}$ benchmark earlier (by `r 155-128` days at SCBI and `r 166-144` at Harvard Forest), and their growth was spread over a longer growing season (average $L_{PGS}$ 22 and 17 days longer at SCBI and Harvard Forest, respectively; Fig. `r DOY_timing`, `r  EDF_growth_curves_all`, `r  EDT_phenology_parameters`).--> 
<!--Peak growing season length was similar across sites, with $L_{PGS}$ being, on average, only six days longer at SCBI for ring porous species and less than one day longer for diffuse porous species (`r  EDT_phenology_parameters`).-->
